
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7: Visualization - Some aspects of ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

-------

Use the data of your own.  Produce the following types of plots and comment on each plot. Plots should be meaningful. If you use the data we used in class, make sure the plots are not the same as the ones in the slides. All plots should have title, caption, appropriate labels on x and y-axis. 

-------

1. Make a plot using `facet_wrap` by one categorical variable (`facet_wrap(~variable1)`)
```{r}
library(tidyverse)
library(knitr)
library(ggplot2)
df <- read_csv('C:/Users/student/OneDrive - Bryant University/Desktop/Statistical_Analysis_with_R/Math421/Math421/21-22BballSeasonData.csv')

df %>% ggplot()+
  geom_point(mapping=aes(x=AVGMIN, y=AVG))+
  facet_wrap(~Position)+
  labs(x='Minutes Per Game',
       y='Points Per Game',
       title='Relationship Between Minutes Per Game and Points 
                       Per Game by Position',
       caption='As minutes per game increases, points per game increases across both positions.')
```

2. Make a plot using `facet_wrap` by two categorical variables (`facet_wrap(~variable1+variable2)`)
```{r}
df %>% ggplot()+
  geom_point(mapping=aes(x=AVGMIN, y=AVG))+
  facet_wrap(~Position+Class)+
  labs(x='Minutes Per Game',
       y='Points Per Game',
       title='Relationship Between Minutes Per Game and Points 
          Per Game by Position and Class Year',
       caption='As minutes per game increases, 
       points per game increases across all class years for both positions.')
```

3. Make a plot using `position ='dodge'`.
```{r}
df %>% ggplot()+
  geom_bar(mapping=aes(x=Class, fill=Position),
           position = 'dodge')+
  labs(x='Class Year',
       y='Count',
       title='Count of Players Across Each Class Year
                        by Position',
       caption='The majority of the team is made up of guards, 
       with 11 of the 15 players being listed as guards.')
```

4. Make a plot using `position ='fill'`. 
```{r}
df %>% ggplot()+
  geom_bar(mapping=aes(x=Class, fill=Position),
           position = 'fill')+
  labs(x='Class Year',
       y='Proportion',
       title='Proportion of Player Position Across Each 
                      Class Year',
       caption='The majority of the team is made up of guards, 
       with over 50% of each undergraduate year 
       being listed as guards.')
```

5. Make a plot using `geom_col`.
```{r}
df %>% group_by(Class) %>% 
  summarise(average_A_TO=mean(A/TO, na.rm=TRUE)) %>% 
  ggplot()+ 
  geom_col(mapping=aes(x=Class, y=average_A_TO))+
  labs(x='Class Year',
       y='Average A/TO',
       title='Average A/TO Ratio by Class Year',
       caption='Freshmen and Junior players have the highest A/TO ratios,
       whereas Sophomore and Graduate players have the lowest A/TO ratios.')
```

6. Change the theme of one of your plots. 
```{r}
df %>% ggplot()+ 
    geom_bar(mapping=aes(x=Class, fill=Position))+
  theme_linedraw()+
  labs(x='Class Year',
       y='Count',
       title='Count of Players Across Each Class Year
                        by Position',
       caption='The majority of the team is made up of guards, 
       with 11 of the 15 players being listed as guards.')
```

7. Make a plot using combo filter + ggplot
```{r}
df %>% 
  filter(GP>20) %>% 
  ggplot()+
  geom_bar(mapping=aes(x=Class, fill=Position))+
  labs(x='Class Year',
       y='Count',
       title='Count of Players Who Have Played At Least 20 
       Games Across Each Class Year by Position',
       caption='The majority of the team is made up of guards, 
       with 11 of the 15 players being listed as guards.')
```

8. Make a plot using combo group_by + summarise + geom_col
```{r}
df %>% 
  group_by(Class, Position) %>% 
  summarise(mean_FGPCT = FGPCT) %>% 
  ggplot()+
  geom_col(aes(x=Class, y=mean_FGPCT, fill=Position), position = 'dodge')+
  labs(x='Class Year',
       y='Avg FG%',
       title='Average FG% Across Each Class Year by Position',
       caption='Forwards have better average FG%s than guards, 
       with the older classes tending to have better
       average FG% than younger classes.')
```

9. Save a plot and put a link of the plot to your Github Webpage.  To link a plot `abc.png` you just need to insert the following on the README.md

```{r}
gg <- df %>% 
  filter(GP>20) %>% 
  ggplot()+
  geom_bar(mapping=aes(x=Class, fill=Position))
ggsave(filename = 'PlayersWithHighGP.png', plot = gg)
```

10. In this question, we will use  the Covid19 vaccination data for the US. The data and data dictionary can be found at the below link:

- [Data](https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations-by-manufacturer.csv)

```{r}
library(tidyverse)
df <- read_csv('https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations-by-manufacturer.csv')
```

`Geom_point` makes scatter plots, which plot two numeric (or Date) variables. A third categorical variable is often brought in for color. For example, we can compare different vaccine types used in the US by

```{r}
df %>% 
  filter(location=='United States') %>% 
  ggplot()+
  geom_point(mapping = aes(x = date, 
                                    y = total_vaccinations,
                                    color = vaccine))+
  labs(x='Date',
       y='Total Vaccinations',
       title='Vaccination Count in the U.S. 
  Over Time by Vaccine Type',
       caption='Pfizer and Moderna grew in popularity very
       rapidly throughout 2021-22, while J&J stayed 
  relatively stagnant.')
```

Do the follows. 

  - Use `geom_point` to compare the vaccines used by date in Argentina in 2022. 
```{r}
df %>% 
  filter(location=='Argentina', date>="2022-01-01", date<"2023-01-01") %>% 
  ggplot()+
  geom_point(mapping = aes(x = date, 
                                    y = total_vaccinations,                                     color = vaccine))+
  labs(x='Date',
       y='Total Vaccinations',
       title='Vaccination Count in Argentina 
    in 2022 by Vaccine Type',
       caption='Cansino, Sputnik V, Oxford/AstraZeneca, and 
       Sinopharm/Beijing stayed relatively stagnant in 
       growth over 2022, while Pfizer/BioNTech and
       Moderna saw strong growth throughout the year.')
```
  
  - Change `geom_point` to `geom_line` in the above codes to have the corresponding line plots. 
```{r}
df %>% 
  filter(location=='Argentina', date>="2022-01-01", date<"2023-01-01") %>% 
  ggplot()+
  geom_line(mapping = aes(x = date, 
                                    y = total_vaccinations,                                     color = vaccine))+
  labs(x='Date',
       y='Total Vaccinations',
       title='Vaccination Count in Argentina 
    in 2022 by Vaccine Type',
       caption='Cansino, Sputnik V, Oxford/AstraZeneca, and 
       Sinopharm/Beijing stayed relatively stagnant in 
       growth over 2022, while Pfizer/BioNTech and
       Moderna saw strong growth throughout the year.')
```

11. (Using the same dataset as in 10.) Sometimes we need to do some calculations on the data before plotting. For example, the below codes is to compare the total vaccines (including all types of vaccines) by date between the US and the EU

```{r}
# the total vaccines (including all types of vaccines) by date
d1 <- df %>% 
  filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE))

# Plot
d1 %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))+
  labs(x='Date',
       y='Total Vaccinations',
       title='Vaccination Count Over Time 
Between the E.U. and the U.S.',
       caption='The U.S. used up more vaccines up until
June 2021, where the E.U. began using more 
vaccines moving forward.')
```

Notice that the above codes could be piped in one 

```{r}
df %>% 
  filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))+
  labs(x='Date',
       y='Total Vaccinations',
       title='Vaccination Count Over Time 
Between the E.U. and the U.S.',
       caption='The U.S. used up more vaccines up until
June 2021, where the E.U. began using more 
vaccines moving forward.')
```


Do the follows. 

- Use `geom_point` to compare the total vaccines (including all types of vaccines) by date between countries/regions in Asia
```{r}
df %>% 
  filter(location %in% c('Cyprus', 'Hong Kong', 'Japan', 'Nepal', 'South Korea')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))+
  labs(x='Date',
       y='Total Vaccinations',
       title='Vaccination Count Over Time 
Between Asian Countries/Regions',
       caption='Japan saw the greatest growth in vaccine
use over time, with every other nation/region other
than South Korea staying relatively stagnant.')
```
- Use `geom_point` to compare the total vaccines (including all types of vaccines) by date between countries/regions in South America in 2021
```{r}
table(df$location)
df %>% 
  filter(location %in% c('Argentina', 'Chile', 'Ecuador', 'Peru'), date>='2021-01-01', date<'2022-01-01') %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))+
  labs(x='Date',
       y='Total Vaccinations',
       title='Vaccination Count in 2021 Between
       South American Countries',
       caption='Argentina and Peru saw relatively consistent
       growth in vaccine use, whereas Chile and
       Ecuador leveled off toward the end of 2021.')
```

