
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 4 - Data Wrangling with `dplyr`"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment4.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- Notice that if there is `eval=FALSE` in the first line of the code chunk, the chunk will not be execute.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 4. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

#### 1. Install `tidyverse` package

An R package can be installed by `install.packages` function. Install `tidyverse` if you have not done so. 

```{r, eval=FALSE}
install.packages('Rtools')
install.packages('tidyverse')
```

-------

#### 2. Read the data using `read.csv`

Use `read.csv` function to import the US Covid 19 data at [link](https://covidtracking.com/data/download/all-states-history.csv).  Don't forget to import `tidyverse` (library(tidyverse)) so that you can use read_csv. 
```{r}
library(tidyverse)
df <- read_csv('https://covidtracking.com/data/download/all-states-history.csv')
```

-------

#### 3.  Fix the date and create some new variables

`lubridate` is a package of the `tidyverse` packages.  We will make uses of `lubridate` in this question.

- Use the below codes to create `month`, `weekday` and `monthday` variables

```{r}
library(lubridate)
df$month = month(df$date)

# day of the week
df$weekday = wday(df$date)

# day of the month
df$monthday <- mday(df$date)
```

-------

#### 4. Create new variables with `case_when`. 

The function `case_when` is a good option to create a new variable from existing variable.  For example, this below codes create a new variable, `daily_death`, from `deathIncrease` variable.  `deathIncrease` is the number of daily new death by Covid19.  The new variable `daily_death` takes three values:  low (if `deathIncrease` less than 3), medium (`deathIncrease` from 3 to 14), and high (`deathIncrease` more than 14).  Please notice that this can also be done in a different way as shown in Assignment 3. 

```{r}
library(tidyverse)
df$daily_death <- case_when(
  df$deathIncrease <3 ~ 'low',
  df$deathIncrease <=14 ~ 'medium',
  TRUE ~ 'high'
)
```

- Create variable `month2` that takes three values: early_month (day of the month from 1-10), mid_month (day of the month from 11-20), and end_month (day of the month > 20).
```{r}
library(tidyverse)
df$month2 <- case_when(
  df$monthday <=10 ~ 'early_month',
  df$monthday <=20 ~ 'mid_month',
  TRUE ~ 'end_month'
)
```

- Create variable `weekend` that takes two values:  1 if it's Saturday or Sunday or 0 otherwise. 
```{r}
library(tidyverse)
df$weekend <- case_when(
  df$weekday <= 5 ~ 0,
  TRUE ~ 1
)
```

-------

#### 5. Select function

Use the select function to deselect the column `totalTestsViral` from the data.
```{r}
df %>% select(-totalTestsViral)
```

-------

#### 6. Pipe Operator ( %>% )

Pipe operator offers another way to write R codes. Many times, it makes the codes more readable.  Pipe works very well with all the `tidyverse` packages. Refer to [these slides](../slides/4_dplyr.html#15) (slide 15, 16, 17 and 18) to rewrite the below codes using pipe operator

```{r}
x <- c(1:10)

# square root of x
# sqrt(x)
x %>% sqrt

# sum(sqrt(x))
x %>% sqrt %>% sum

# log(sum(sqrt(x)))
x %>% sqrt %>% sum %>% log

# log base 2 of 16
# log(16, 2)
16 %>% log2
```

-------

#### 7. Combo 1: group_by + summarise

This combo is used when you want to apply a function/calculation to different groups of the data. For example, to calculate the average number of cases (`positiveIncrease`) by `dataQualityGrade`, we use:

```{r}
df %>% 
  group_by(weekday) %>% 
  summarise(mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) by `month`
```{r}
df %>% 
  group_by(month) %>% 
  summarise(median(positiveIncrease))
```

- Calculate the average number of cases (`positiveIncrease`) by `month2`
```{r}
df %>% 
  group_by(month2) %>% 
  summarise(mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) by `weekend`
```{r}
df %>% 
  group_by(weekend) %>% 
  summarise(median(positiveIncrease))
```


-------

#### 8. Combo 2: filter + group_by + summarise

An example: to calculate the average number of cases (`positiveIncrease`) in January and February separately, we use:

```{r}
df %>% 
  filter(month==1|month==2) %>% 
  group_by(month) %>% 
  summarise(positive_increase = mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) on the weekend by `month` in October and November 2020. 
```{r}
df %>% 
  filter(month==10|month==11) %>% 
  group_by(month) %>% 
  summarise(positive_increase = median(positiveIncrease))
```

- Calculate the average number of death at different periods of a month (`month2` variable) in Fall 2020
```{r}
df %>% 
  filter(month==9|month==10|month==11) %>% 
  group_by(month2) %>% 
  summarise(positive_increase = mean(positiveIncrease))
```

- Compare the average number of hospitalizations between weekdays and weekends in Summer 2020
```{r}
df %>% 
  filter(month==6|month==7|month==8) %>% 
  group_by(weekend) %>% 
  summarise(hospitalizedIncrease = mean(hospitalizedIncrease))
```

- Redo Questions 14 and 15 in [Assignment 3](assignment3.html) using the combos.  Notice:  you also need to use the data used in Assignment 3.  
```{r}
q2 <- read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv')

q2$date <- as.Date(q2$date)
q2$weekdays <- weekdays(q2$date)
q2 %>% 
  filter(state=='Rhode Island'|date>='2021-01-01'|date<'2022-01-01') %>% 
  group_by(weekdays) %>% 
  summarise(cases = median(cases))
```

-------

#### 9. Combo 3: filter + group_by + summarise + arrange

Use the arrange function to find a month that has the highest number of deaths on the weekend. 
```{r}
df %>% 
  filter(weekend==1) %>% 
  group_by(month) %>% 
  summarise(max_deaths = max(deathIncrease)) %>% 
  arrange(-max_deaths)
```

-------

#### 10. Use your own dataset and implement the follows functions or combos. You can use the [Adult Census Income](../data/adult_census.csv) or [Titanic data](../data/titanic.csv). 

- select
- filter
- mutate
- summarise
- arrange
- count
- count + arrange
- filter + count + arrange
- group_by + summarise
- filter + group_by + summarise
- filter + group_by + summarise + arrange
```{r}
library(tidyverse)
adult_data <- read_csv('https://bryantstats.github.io/math421/data/adult_census.csv')

# Selecting the age, education, and income variables
adult_data %>% select(age, education, income)

# Filtering data to show divorced adults who work 40 hours per week
adult_data %>% filter(marital.status=='Divorced',hours.per.week==40)

# Calculating an income column
adult_data %>% mutate(income = capital.gain - capital.loss)

# Summarise the mean, median, and max hours per week
adult_data %>% summarise(mean_hours = mean(hours.per.week, na.rm = TRUE),
                         median_hours = median(hours.per.week, na.rm = TRUE),
                         max_hours = max(hours.per.week, na.rm = TRUE))

# Arrange the age variable in descending order
adult_data %>% 
  arrange(-age)

# Show count of education types
adult_data %>% 
  count(education)

# Arrange count of education types in descending order
adult_data %>% 
  count(education) %>% 
  arrange(-n)

# Filter count of education types by only female adults and arrange in descending order
adult_data %>% 
  filter(sex=='Female') %>% 
  count(education) %>% arrange(-n)

# Group adults by relationship type and summarise each group's mean hours worked per week
adult_data %>% 
  group_by(relationship) %>% 
  summarise(mean(hours.per.week))

# Group adults with degrees higher than high school by education and summarise each group's mean hours worked per week
table(adult_data$education)
adult_data %>%   
  filter(education=='Assoc-acdm'|education=='Assoc-voc'|education=='Bachelors'|education=='Doctorate'|education=='Masters'|education=='Prof_school') %>% 
  group_by(education) %>% 
  summarise(mean_hours_per_week = mean(hours.per.week))

# Group adults with degrees higher than high school by education and summarise each group's mean hours worked per week in descending order
adult_data %>%
  filter(education=='Assoc-acdm'|education=='Assoc-voc'|education=='Bachelors'|education=='Doctorate'|education=='Masters'|education=='Prof_school') %>% 
  group_by(education) %>% 
  summarise(mean_hours_per_week = mean(hours.per.week)) %>%
  arrange(-mean_hours_per_week)
```

