
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Universal Framework"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment11.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Install the package mlbench and use the follows to import the data

```{r}
library(mlbench)
library(tidyverse)
data(PimaIndiansDiabetes)
df <- tibble(PimaIndiansDiabetes)
```

Train and Test a decision tree and a random forest with caret. Plot the variable importance of these models. 
```{r}
library(caret)
df <- df %>% rename(target=diabetes)
df <- df %>% 
  mutate(target = as.factor(target))
splitIndex <- createDataPartition(df$target, p = .70, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
model <- train(target ~ ., data=df_train, 
                method = "rpart2",
                maxdepth=3)
pred <- predict(model, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]

modelF <- train(target~., data=df_train, 
                method = "rf",
                ntree = 1000) 
predF <- predict(modelF, df_test)
cmF <- confusionMatrix(data = predF, reference = df_test$target)
cmF$overall[1]

varImp(model)
varImp(modelF)
plot(varImp(model))
plot(varImp(modelF))
```

2. Train and Test a `glmnet` model. Plot the variable importance of the model. 
```{r}
library(glmnet)
model2 <- train(target ~ ., data=df_train, 
                method = "glmnet")
pred2 <- predict(model2, df_test)
cm2 <- confusionMatrix(data = pred2, reference = df_test$target)
cm2$overall[1]

varImp(model2)
plot(varImp(model2))
```

3. Train and test two models that are not `ranger`, `glmnet` or `rpart`  with caret. If possible, plot the variable importance of the model.
```{r}
library(arm)
model3 <- train(target ~ ., data=df_train, 
                method = "bayesglm")
pred3 <- predict(model3, df_test)
cm3 <- confusionMatrix(data = pred3, reference = df_test$target)
cm3$overall[1]

library(rpart)
model4 <- train(target ~ ., data=df_train, 
                method = "rpart1SE")
pred4 <- predict(model4, df_test)
cm4 <- confusionMatrix(data = pred4, reference = df_test$target)
cm4$overall[1]

varImp(model4)
plot(varImp(model4))
```

