
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14: Twitters Mining with rtweet"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment14.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


[Sample Codes](https://bryantstats.github.io/math421/slides/16_text_mining_rtweet.html)

-------

1. Pick a keyword or hashtag. Download the data associated with the keyword/hashtag. Plot at least 5 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r}
library(rtweet) 
library(tidytext)
library(ggpubr) 
library(tidyverse) 
library(knitr)
library(lubridate)

#auth_setup_default()

keyword_search = '#worldwar3'

df <- search_tweets(q = keyword_search, 
                        n = Inf, # number of tweets
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% 
  mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

write_csv(df, 'twitter_data.csv')


# Plot 1: Frequency of Tweets by Time

ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of #worldwar3 Tweets by Time",
       subtitle = paste0(format(min(df$created_at), "%d %B %Y"), " to ", format(max(df$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()


# Plot 2: Top Emojis in the Tweets

#install.packages("devtools")
#devtools::install_github("hadley/emo")

library(emo)
df %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(x = 'Top Emojis in the Tweets', y = '')


# Plot 3: Hashtag Cloud

#install.packages('RColorBrewer')
library(RColorBrewer)

pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

df %>% 
  filter(created_at>='2022-11-14') %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#worldwar3", "#worldwariii", "#ww3", "wwiii"), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  filter(hashtag != 'mufc') %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))


# Plot 4: Mentions

df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10)

df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(x = 'Top 10 Mentions in the Tweets', y = '')


# Plot 5: Sentiment Analysis

df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='')
```

2. Choose a location then pick a trending keyword/hashtag in the location. Download the data associated with the keyword/hashtag. Plot at least 5 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r}
# Show available locations to get trends
trends_available()

# See World wide trends twits
get_trends('Toronto')

keyword_search = '#RIPJimmyFallon'

df <- search_tweets(q = keyword_search, 
                        n = Inf, # number of tweets
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% 
  mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

write_csv(df, 'twitter_data.csv')

# Plot 1: Frequency of Tweets by Time

ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of #RIPJimmyFallon Tweets by Time",
       subtitle = paste0(format(min(df$created_at), "%d %B %Y"), " to ", format(max(df$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()


# Plot 2: Top Emojis in the Tweets

#install.packages("devtools")
#devtools::install_github("hadley/emo")

library(emo)
df %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(x = 'Top Emojis in the Tweets', y = '')


# Plot 3: Hashtag Cloud

#install.packages('RColorBrewer')
library(RColorBrewer)

pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

df %>% 
  filter(created_at>='2022-11-14') %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#RIPJimmyFallon", "ripjimmyfallon", "JimmyFallon", "Jimmy", "jimmy", "Fallon", "fallon'"), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  filter(hashtag != 'mufc') %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))


# Plot 4: Mentions

df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10)

df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(x = 'Top 10 Mentions in the Tweets', y = '')


# Plot 5: Sentiment Analysis

df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='')
```
