
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 10: Predictive Modeling - Part 1"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment10.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Use the `Adult Census Income` dataset.  We will predict the income (whether or not it is more than 50k or not) of an adult. Import the dataset.  Partition the data into 80% training and 20% testing.  
```{r}
#install.packages('caret', dependencies = TRUE)
#install.packages('createDataPartition', dependencies = TRUE)

library(tidyverse)
library(caret)
df <- read_csv('C:/Users/student/OneDrive - Bryant University/Desktop/Statistical_Analysis_with_R/Math421/Math421/adult_census.csv')

df <- df %>% rename(target=income)

df <- df %>% 
  mutate(age = age,
         workclass = as.factor(workclass),
         fnlwgt = fnlwgt,
         education = as.factor(education),
         education.num = education.num,
         marital.status = as.factor(marital.status),
         occupation = as.factor(occupation),
         relationship = as.factor(relationship),
         race = as.factor(race),
         sex = as.factor(sex),
         capital.gain = capital.gain,
         capital.loss = capital.loss,
         hours.per.week = hours.per.week,
         native.country = as.factor(native.country),
         target = as.factor(target)
         )

set.seed(2020)
splitIndex <- createDataPartition(df$target, p = .80,
                                  list = FALSE)

df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```

2. Practice Decision Tree.  Do the follows:

  - Use `rpart` package, create a decision tree with maximum depth of 3. 
  
  - Calculate the accuracy of the model on the testing data. Notice that the positive outcome here is not `1` but `>50K` or `<50K`. 
  
  - Plot the tree
  
  - Plot the variable importance by the tree
```{r}
#install.packages('rattle')
library(rpart)
library(rattle)
tree_model <- rpart(target ~ ., data = df_train,
                    control = rpart.control(maxdepth = 3))
pred <- predict(tree_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = ">50K")
cm$overall[1]

fancyRpartPlot(tree_model)
barplot(tree_model$variable.importance)
```
  
3. Create 3 more trees and compare the testing accuracy of these trees, which tree give the highest testing accuracy.
```{r}
tree_model1 <- rpart(target ~ ., data = df_train,
                    control = rpart.control(maxdepth = 1))
pred1 <- predict(tree_model1, df_test, type = "class")
cm1 <- confusionMatrix(data = pred1, reference = df_test$target, positive = ">50K")

tree_model2 <- rpart(target ~ ., data = df_train,
                    control = rpart.control(maxdepth = 2))
pred2 <- predict(tree_model2, df_test, type = "class")
cm2 <- confusionMatrix(data = pred2, reference = df_test$target, positive = ">50K")

tree_model3 <- rpart(target ~ ., data = df_train,
                    control = rpart.control(maxdepth = 4))
pred3 <- predict(tree_model3, df_test, type = "class")
cm3 <- confusionMatrix(data = pred3, reference = df_test$target, positive = ">50K")

cm1$overall[1]
cm2$overall[1]
cm3$overall[1]
```

4. Practice Random Forest.  Do the follows: 

  - Use `randomForest` package, create a random forest of 1000 trees. 
  
  - Calculate the accuracy of the model on the testing data. 
  
  - Plot the variable importance by the forest
```{r}
library(randomForest)
forest_model = randomForest(target ~ ., data=df_train, ntree = 1000)
predF <- predict(forest_model, df_test, type = "class")
cmF <- confusionMatrix(data = predF, reference = df_test$target)
cmF$overall[1]
```
  
5. Create 3 more forests and compare the testing accuracy of these forests, which forest give the highest testing accuracy.
```{r}
forest_model1 = randomForest(target ~ ., data=df_train, ntree = 500)
predF1 <- predict(forest_model1, df_test, type = "class")
cmF1 <- confusionMatrix(data = predF1, reference = df_test$target)

forest_model2 = randomForest(target ~ ., data=df_train, ntree = 1500)
predF2 <- predict(forest_model2, df_test, type = "class")
cmF2 <- confusionMatrix(data = predF2, reference = df_test$target)

forest_model3 = randomForest(target ~ ., data=df_train, ntree = 2000)
predF3 <- predict(forest_model3, df_test, type = "class")
cmF3 <- confusionMatrix(data = predF3, reference = df_test$target)

cmF1$overall[1]
cmF2$overall[1]
cmF3$overall[1]
```

6. What is the best model (in term of testing accuracy) among all models (including trees and forests) you have trained?
```{r}
cmF$overall[1]
```

