---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***:

-   Open the Rmarkdown file of this assignment ([link](assignment8.Rmd)) in Rstudio.

-   Right under each **question**, insert a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question.

-   `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.

-   Publish the html file to your Githiub Page.

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

------------------------------------------------------------------------

1.  Install two packages `gganimate` and `gifski` then restart Rstudio. Using the `Adult Census Income` data, make an animation using `geom_point` and `transition_states`.

```{r}
#install.packages('gganimate')
#install.packages('gifski')
library(gganimate)
library(gifski)
library(ggplot2)
library(tidyverse)
library(knitr)
df <- read_csv('C:/Users/student/OneDrive - Bryant University/Desktop/Statistical_Analysis_with_R/Math421/Math421/adult_census.csv')

df %>% ggplot(aes(x = hours.per.week, y = age, color=sex))+
  geom_point()+
  transition_states(race)+
  labs(title = 'Race: {closest_state}')
```

2.  Using the `Adult Census Income` data, make an animation using `geom_bar` and `transition_states`.

```{r}
library(gganimate)
library(gifski)
library(ggplot2)
library(tidyverse)
library(knitr)

df %>% ggplot(aes(x = race, fill=sex))+
  geom_bar()+
  transition_states(education)+
  labs(title = 'Education: {closest_state}')
```

3.  Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19 in 2021.

```{r}
library(gganimate)
library(gifski)
library(ggplot2)
library(tidyverse)
library(knitr)
library(lubridate)

df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')

df <- df %>% filter(Date_reported>='2021-01-01'|Date_reported<'2022-01-01')
df$Month <- month(df$Date_reported)
d1 <- df %>% group_by(Month, Country) %>% summarise(mean = mean(Cumulative_deaths))
d2 <- d1 %>% group_by(Month) %>% mutate(rank=rank(-mean)) 
d3 <- d2 %>% filter(rank <= 10)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col()+
    geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Month {closest_state}', x='', y='Total Number of Deaths', fill='Country')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(Month)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```

4.  Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (<https://covidtracking.com/data/download/all-states-history.csv>) but you should make a different bar race from ones in the slides.
```{r}
library(gganimate)
library(gifski)
library(ggplot2)
library(tidyverse)
library(knitr)

df <- read_csv('C:/Users/student/OneDrive - Bryant University/Desktop/Statistical_Analysis_with_R/Math421/Math421/21-22BballSeasonData.csv')

df <- df %>% filter(GP>=20)
d1 <- df %>% group_by(Class, Position) %>% summarise(mean = mean(FGPCT))
d2 <- d1 %>% group_by(Class) %>% mutate(rank=rank(-mean)) 
d3 <- d2 %>% filter(rank <= 10)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Position, fill=Position, label=Position)) + geom_col()+
    geom_text(aes(y = mean, label = Position), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Class {closest_state}', x='', y='Average FG%', fill='Position')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(Class)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```