
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|
```{r}
df <- data.frame(Rank = c(0,1,2,3),
                 Age = c(28,34,29,42),
                 Name = c('Tom','Jack','Steve','Ricky'))
df
```

2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).
```{r}
q2 <- read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv')
```

2. Show the names of the variables in the data
```{r}
names(q2)
```

3. How many columns and rows does the data have? 
```{r}
str(q2)
```

4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?
```{r}
sum(is.na(q2))
colSums(is.na(q2))
```

5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 
```{r}
class(q2$date)
q2$date <- as.Date(q2$date)
class(q2$date)
```

6. Capitalize the names of all the variables
```{r}
names(q2)[names(q2) == 'date'] <- 'Date'
names(q2)[names(q2) == 'state'] <- 'State'
names(q2)[names(q2) == 'fips'] <- 'Fips'
names(q2)[names(q2) == 'cases'] <- 'Cases'
names(q2)[names(q2) == 'deaths'] <- 'Deaths'
names(q2)
```

7. Find the average number of cases per day. Find the maximum cases a day.  
```{r}
mean(q2$Cases, na.rm=TRUE)
max(q2$Cases, na.rm=TRUE)
```

8. How many states are there in the data?  
```{r}
table(q2$State)
length(table(q2$State))
```

9. Create a new variable `weekdays` to store the weekday for each rows. 
```{r}
q2$Weekdays <- weekdays(q2$Date)
```

10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day

Find the frequency and relative frequency of `no_death` and `has_death`. 
```{r}
q2$death2 <- ifelse(q2$Deaths>0,"has_death","no_death")
table(q2$death2)

freq <- table(q2$death2)
freq
rf <- table(q2$death2)/length(q2$death2)
rf
```

11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)
```{r}
summary(q2$Deaths)
```

12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3
```{r}
library(tidyverse)
q2$death3 <- case_when(q2$Deaths<=846 ~ 'low_death',
                    q2$Deaths<=4101 ~ 'mid_death',
                    TRUE ~ 'high_death')
table(q2$death3)
```

13. Find the average cases in Rhode Island in 2021
```{r}
df1 <- q2[(q2$State=='Rhode Island')&(q2$Date>='2021-01-01')&(q2$Date<'2022-01-01'),]
mean(df1$Cases)
```

14. Find the median cases by weekdays in Rhode Island in 2021 
```{r}
df2 <- q2[(q2$State=='Rhode Island'),]
by(q2$Cases,q2$Weekdays,median)
```

15. Compare the median cases in Rhode Island in June, July, August and September in 2021. 
```{r}
df3 <- q2[(q2$State=='Rhode Island')&(q2$Date>='2021-06-01')&(q2$Date<'2021-10-01'),]
df3$Month <- substr(df3$Date,6,7)
by(df3$Cases,df3$Month,median)
```

16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when
```{r}
dataset <- read.csv('C:/Users/student/OneDrive - Bryant University/Desktop/Statistical_Analysis_with_R/Math421/Math421/21-22BballSeasonData.csv')

# Quick preview of the 2021-22 Bryant Men's Basketball dataset
head(dataset)

# Labeling each variable type
str(dataset)

# Listing the name of each variable (columns)
names(dataset)

# Mean Team FG% Calculation
mean(dataset$FGPCT)

# Minimum Team A/TO ratio
min(dataset$A.TO)

# Maximum Number of Minutes Played for a single player
max(dataset$MIN)

# Table list of Team Roster
table(dataset$Player)

# Check to see if there are any null values in the dataset
is.na(dataset)

# Column summary of number of null values for each variable
colSums(is.na(dataset))

# Class type for 'No.' variable (Player Number)
class(dataset$No.)

# Calculating correlation between minutes played and points scored
cor(dataset$MIN, dataset$PTS)

# Evaluate average number of minutes played based on disqualification count
by(dataset$AVGMIN, dataset$DQ, FUN = mean)

# Efficiency variable creation to determine which players have a A/TO ratio less than 1.0
dataset$EFF <- ifelse(dataset$A.TO<1.0,"efficient","inefficient")
table(dataset$EFF)

# Ranking players into 3 tiers based on minutes played
library(tidyverse)
dataset$Workload <- case_when(dataset$MIN<=500 ~ 'low_workload',
                    dataset$MIN<=1000 ~ 'mid_workload',
                    TRUE ~ 'high_workload')
table(dataset$Workload)
```

17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)
```{r}
# Efficiency variable creation to determine which players have a A/TO ratio less than 1.0
dataset$EFF <- ifelse(dataset$A.TO<1.0,"efficient","inefficient")
table(dataset$EFF)

# Ranking players into 3 tiers based on minutes played
library(tidyverse)
dataset$Workload <- case_when(dataset$MIN<=500 ~ 'low_workload',
                    dataset$MIN<=1000 ~ 'mid_workload',
                    TRUE ~ 'high_workload')
table(dataset$Workload)
```

