
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Handle Missing Values"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment5.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use `read_csv` to import the data.  Show the number of NAs for each columns.
```{r}
library(tidyverse)
df <- read_csv('C:/Users/student/OneDrive - Bryant University/Desktop/Statistical_Analysis_with_R/Math421/Math421/adult_census_missing.csv')

colSums(is.na(df))
```

2. Using function `aggr` the VIM package to plot the number of NAs for each column. 
```{r}
#install.packages('VIM')
library(VIM)
aggr(df)
```

3. Find other forms of missing values. Hint: You can use the `table` function to check if there are suspicious categories (Unknown, for example) in a variable. What are all other forms of missing values shown in the data. 
```{r}
table(df$workclass)
table(df$education)
table(df$marital.status)
table(df$occupation)
table(df$relationship)
table(df$race)
table(df$sex)
table(df$native.country)

#Other forms of Missing values: ?, Not Known, Unknown
```

4. Replace all the forms of missing values found to NA
```{r}
df <- df %>% na_if('?') %>% na_if('Not Known') %>% na_if('Unknown')
```

5. Replot the number of NAs for each column. 
```{r}
aggr(df)
```

6. Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs).  How many rows left after removing?
```{r}
dfApproach1 <- drop_na(df)
dfApproach1
```

7. Approach 2 to handle NAs:  Fill all the NAs with the previous or next value. (Hint: Using `fill` function).  Save the dataset after filling as a different data. The original data is unchanged (still have NAs). 
```{r}
colSums(is.na(df))
dfApproach2 <- df %>% fill(age, workclass, education, marital.status, occupation, relationship, sex, capital.gain, native.country, .direction = 'updown')
```

8. Approach 3 to handle NAs: For numeric variable, replace the NAs by the median.  For categorical variables, replace the NAs to the majority. 
```{r}
median_age <- median(df$age, na.rm = TRUE)
df$age <- replace_na(df$age, median_age)

majority_workclass <- names(which.max(table(df$workclass)))
df$workclass <- replace_na(df$workclass, majority_workclass)

majority_education <- names(which.max(table(df$education)))
df$education <- replace_na(df$education, majority_education)

majority_marital.status <- names(which.max(table(df$marital.status)))
df$marital.status <- replace_na(df$marital.status, majority_marital.status)

majority_occupation <- names(which.max(table(df$occupation)))
df$occupation <- replace_na(df$occupation, majority_occupation)

majority_relationship <- names(which.max(table(df$relationship)))
df$relationship <- replace_na(df$relationship, majority_relationship)

majority_sex <- names(which.max(table(df$sex)))
df$sex <- replace_na(df$sex, majority_sex)

median_capital.gain <- median(df$capital.gain, na.rm = TRUE)
df$capital.gain <- replace_na(df$capital.gain, median_capital.gain)

majority_native.country <- names(which.max(table(df$native.country)))
df$native.country <- replace_na(df$native.country, majority_native.country)
```





